Oregon_manuscript

### 2017-10-31 r_scripts/analysis/Oregon_manuscript.Rmd
Create Oregon_manuscript.Rmd
Manuscript

@@

```{r library, include=FALSE, echo=FALSE}
library(tidyverse)
# library(data.table)
library(survival)
library(ggplot2)
library(htmlTable)
library(knitr)
library(broom)
library(lme4)
library(maps)
library(lubridate) # date
library(ggrepel)
library(sp)
library(cowplot)

@@

**1. Introduction: **
We already found an association with wildfire smoke and respiratory outcomes in Washington state in 2012 wildfire season using a novel estimate of smoke concentration, geo-graphically weighted ridge regression (GWR). We want to know if smoke impacts other health outcomes, specifically respiratory rescue medications (beta 2 agonists) (abbreviate to SABA)

For this research we have the Oregon All Payer All Claims (APAC) data set in 2013. We want to research on the effects of wildfire smoke on beta-2 agonist pharmacy fill, a medication primarily used as a rescue medication for persons with asthma or COPD. NDC (National Drug Code) is the variable in the data set that the data set offered. The standard NDC I use is shown in the link below, which is a ndc list in 2013 and fits the original data set after checking. 
(http://ww2.ncqa.org/hedis-quality-measurement/hedis-measures/hedis-2013/hedis-2013-final-ndc-lists)

@@

The data cleaning and creation of the casecross-over dataframes are huge computation tasks, so they are done with server, the following work is done with local R. We analyze the case crossover results with overall pharmacy fills, and analyze the results with age strarified and sex stratified categories for the pharmacy fills in supplement. We also analyze with the distributed lag method, and check with time series analysis.

In these comparisons, we examine GWR method of smoke PM2.5 estimations and associations with medication outcomes using a time-stratified case-crossover study design. Pharmacy outcomes for a patient with a primary diagnosis of all pharmacy records from Oregon state are recorded, and we also have APAC data for people that were billed for a cardiopulmonary event that we can link to the pharmacy claims, in which their dates of admission (index time) are also identified. We then created counterfactual observations for each patient on the same day of the week during the entire wildfire season (May 1st to Sep 30th, 2013). For patients who have a index time before May 1, 2013 or after September 30, 2013, their referent observations before or after these dates will be excluded because we are not able to assign estimates of PM2.5 to these observations.

@@

There are about 77 million claims in the total data set, of which 23 million are pharmacy records denoted by the NDC variable. So we choose the claims in Oregon State with ndc existing, which is about 23 million claims. Also, the POS (Place of service code) all show "pharmacy" type, comparing to the previous health disease outcomes we limit the "emergency visit" type and the "urgent care" type.

For ndc, we choose the people who were billed for filling a beta2 agonist prescription, which we use as a proxy for use to form the sample. Because the ndc csv file has more information than what we need, we filter the ndc file by SQLite Studio (code and steps not attached) to a file only containing the beta 2 agonists medication information.

After choosing the claims with beta 2 agonists, the data set is reduced to 232,665 observations. After first recorded pharmacy fill and limit the wildfire season dates (May 1st, 2013 to September 30th, 2013), the data set is the final data set for analysis, which contains 24,538 beta2 agonist records.

@@

For our research question, we focus on the GWR method (geographically weighted ridge regression). For Geo-Weighted Regression model, with 'smk' designator, we subtracted off the 'Background' estimates of smoke, which are the monthly averages of PM2.5 for a given grid. However, the 'Background' is the mean of total period from May 1st to Sep 30th 2013 so we have to assign the mean smoke estimates for every day.

@@

To analyze the result, we use the conditional logistic regression model using the survival package in R. Each conditional logistic regression model accounts for the subject, and adjusts for temperature from the GWR smoke model. The conditional logistic regression model \beta represents the change in risk of an pharmacy event associated with a short-term unit increase in exposure, and can be calculated as an average difference between exposure at the index time and a weighted average of exposure at all times in the referent window. (???)

@@

The time-stratified casecross-over design uses subjects as their own controls. For each pharmacy claim, we also created counterfactual observations on the the same day of the week over the study period for each subject to indicate the outcome for this day is "1". Then I make the dates week by week before this date, and after this date in the whole wildfire season, and indicate these dates' outcomes are "0". Then I can use these outcomes for the following regression model building.

@@

Also, to get the time stratified data set, I create the lag variables that take smoke values from the previous days for zip codes, joined with the zipcode level populatoin-weighted pm to the data set, and create age, sex, month and season index.

@@

I also make time stratified time series data set. The original data set only contains the zip code, but for time series, we want to research on the county level. Therefore, I assign each zip code with one county which I found online. There are 488 zipcodes in total (4 are missing but I use google to find the relavent county). This is a sensitivity analysis to check and confirm the casecross over results.

@@

@@

The map shows

@@

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle(expression("Oregon: 2013 Fire Season Smoke PM"[2.5])) +
   theme(legend.position="none") +
   # theme(axis.text.x=element_blank()) +
  theme(panel.background = element_rect(fill = 'white', colour = 'white')) +
  theme(strip.background = element_rect(colour = "white", fill = "white"))+
  ylab(expression(paste("GWR Smoke PM"[2.5], " Concentration, µg/m^3" ))) +
  xlab("May 1st to Sep 30th in 2013") +
  theme(axis.line.x = element_line(color="black"),
        axis.line.y = element_line(color="black"))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

# smoke days where GWR smoke > 15
smoke_map <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#3964C3", high = "#dc2430") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
   theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties Affected by Smoke PM2.5 > 10µg/m^3") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA)) +
  geom_text_repel(data = centroids, aes(long, lat, label = rownames(centroids), group=NULL), size = 2.5)

smoke_map1 <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#3964C3", high = "#dc2430") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
   theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties Affected by Smoke PM2.5 > 10µg/m^3") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA)) +
  geom_text(data = centroids, aes(long, lat, label = rownames(centroids), group=NULL), size = 2)

@@

For all of 2013, there were a total of 77 millon claim records in the APAC dataset. During the May 1st to September 30th wildfire season in Oregon state, there were 24217 pharmacy visits for the ndc of beta 2 agonists. The number of cases, as well as age-specific and sex-specific strate are shown below.

@@

### Outcomes of four kinds

@@

The overall plot shows that when smoke concentration increases 10ug/m^3, the risk to get beta-2 agonist fill will increase about 7.5% significantly.

@@

The plot shows that four different categories

@@

Although the casecrossover study shows a significant association of getting beta-2 agonist pharmacy fills and smoke concentration, we still wonder the association of the pharmacy fills with some lag days. For medication analysis, people could get the pharmacy fills one or some days later than the day they find they have the disease. Then we make 0 (the original day) to 7 lags (one week) to see association of pharmacy fills with different lagged days.

@@

When choosing the df of 5, the plot shows that the same day of fill with smoke exposure has the highest significant association. But other lags shows that pharmacy fills with lagged days do not has the significant association with smoke. And the association tends to decrease as lag goes.

@@

```{r DLM for disease respiratory, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease asthma, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease pneumonia, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease acute_bronch, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease copd, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease cvd, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease isch_heart_dis, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease arrhythmia, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease heart_failure, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease cerbrovas_dis, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease myocardial_infarc, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r DLM for disease broken_arm, echo = FALSE, message=FALSE, warning=FALSE}

@@

```{r}
plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, ncol=4)

>>>>

---
title: "Oregon_manuscript"
author: "Jingyang Liu"
date: "2017/10/30"
output: html_document
---

@@

```{r library, include=FALSE, echo=FALSE}
library(tidyverse)
# library(data.table)
library(survival)
library(ggplot2)
library(htmlTable)
library(knitr)
library(broom)
library(lme4)
library(maps)
library(lubridate) # date
library(ggrepel)
library(sp)
library(cowplot)
library(geofacet)

@@

**1. Introduction: **
This data set of sample population for our research come from the Oregon All Payer All Claims Database (APAC) in the year 2013, which recorded the health care data for Oregon’s insured populations. This database included our main researched aspects, which are individuals with both disease and pharmacy claims. The disease codes were International Classification of Diseases, Clinical Modification (ICD-9-CM) diagnoses codes, and the pharmacy codes were National Drug Codes (NDC).

We already found an association with wildfire smoke and respiratory outcomes in Washington state in 2012 wildfire season using a novel estimate of smoke concentration, geographically weighted ridge regression (GWR). We wanted to know if smoke impacts other health outcomes, specifically respiratory rescue medications (beta 2 agonists) (abbreviate to SABA). However, we did not have the specific NDC for asthma or respiratory, then we transfered to find the SABA instead and made categories for different diseases.

@@

We limited the population to patients whose admission date are during the wildfire season (May 1 to September 30, 2013) within Oregon State, and checked the zip codes of these patients. We further limited the population who were billed for filling a SABA prescription, which we used as a proxy for use. Finally, we limited to the subjects of the unique patient’s first visit to reduce the potential bias of counting a event multiple times.

In these comparisons, we examined GWR method of smoke PM2.5 estimations and associations with medication outcomes using a time-stratified case-crossover study design. Pharmacy outcomes for a patient with a primary diagnosis of all pharmacy records from Oregon state were recorded, and we also had APAC data for people who were billed for a cardiopulmonary event that we could also link the disease to the pharmacy claims, in which their dates of admission (index time) were also identified. We then created counterfactual observations for each patient on the same day of the week during the entire wildfire season for Oregon.

@@

There were about 77 million claims in the total data set, of which 23 million were pharmacy records denoted by the NDC variable. So we chose the claims in Oregon State with ndc existing, which was about 23 million claims. Also, the POS (Place of service code) all showed "pharmacy" type, comparing to the previous health disease outcomes we limited the "emergency visit" type and the "urgent care" type.

For ndc, we chose the people who were billed for filling a beta2 agonist prescription, which we used as a proxy for use to form the sample. Because the ndc csv file had more information than what we need, we filtered the ndc file by SQLite Studio to a file only containing the beta 2 agonists medication information for filtering patients.

After choosing the claims with beta 2 agonists, the data set was reduced to about 232 thousand observations. After first recorded pharmacy fill and limit the wildfire season dates (May 1st, 2013 to September 30th, 2013), the data set was the final data set for analysis, which contained 24,538 beta-2 agonist records.

@@

For our research question, we focused mainly on the GWR method (geographically weighted ridge regression). For Geo-Weighted Regression model, with 'smk' designator, we subtracted off the 'Background' estimates of smoke, which were the monthly averages of PM2.5 for a given grid. However, the 'Background' given was the mean of total period from May 1st to Sep 30th 2013 so we had to assign the mean smoke estimates for every day. For patients who had a index time before May 1, 2013 or after September 30, 2013, their referent observations before or after these dates would be excluded because we were not able to assign estimates of PM2.5 to these observations by atmospheric department.

@@

To analyze the result, we used the conditional logistic regression model using the survival package in R. Each conditional logistic regression model accounted for the subject, and adjusted for temperature from the GWR smoke model. The conditional logistic regression model  represented the change in risk of an pharmacy event associated with a short-term unit increase in exposure, and could be calculated as an average difference between exposure at the index time and a weighted average of exposure at all times in the referent window. (???)

We also used distributed lag model because we still wondered the association of the pharmacy fills with some lag days. For medication analysis, people could get the pharmacy fills one or some days later than the day they find they have the disease. Then we made 0 (the original day) to 7 lags (one week) to see association of pharmacy fills with different lagged days.

@@

The time-stratified case-crossover design used subjects as their own controls. For each pharmacy claim, we also created counterfactual observations on the the same day of the week over the fire season for each subject to indicate the outcome for this day was "1". Then we made the dates week by week before this date, and after this date in the whole wildfire season, and indicated these dates' outcomes were "0". Then we could use these outcomes for the following regression model building.

@@

Also, to get the time stratified data set, we created the lag variables that take smoke values from the previous days for zip codes, joined with the zip code level population-weighted pm to the data set, and create age, sex, month and season index.

@@

I also make time stratified time series data set. The original data set only contains the zip code, but for time series, we want to research on the county level. Therefore, I assign each zip code with one county which I found online. There are 488 zip codes in total (4 are missing but I use google to find the relevant county). This is a sensitivity analysis to check and confirm the case-crossover results.

Since the data cleaning and creation of the data frames for case-crossover study were huge computation tasks, the cleaning work was done with Linux server, the following work was done with local R and packages, such as ggplot2, survival and lme4, etc. We analyzed the case-crossover results with overall pharmacy fills, and analyzed the results with age stratified and sex stratified categories for the pharmacy fills in supplemental materials. We also analyzed with the distributed lag method, and also checked with time series analysis in supplemental materials.

@@

Figure 1 shows the range of county population-weighted PM2.5 concentrations of smoke for GWR method from May 1 to September 30, 2013 in Oregon State counties. Most of the counties showed almost flat trends of smoke concentration while a few showed a sharp increase during late July to late August.

@@

Figure 2 showed the number of smoke-impacted days in Oregon State counties from May 1 to September 30, 2013. Southwest region had the highest number of smoke-impacted days during this wildfire season.

@@

or_smk_plot <- ggplot(or_smk, aes(x = date, y = pm)) +
  geom_point(aes(colour = smk_method), alpha = 0.8, size = 0.8) +
  facet_wrap(~county) +
  ggtitle(expression("Oregon: 2013 Fire Season Smoke PM"[2.5])) +
   theme(legend.position="none") +
   # theme(axis.text.x=element_blank()) +
  theme(panel.background = element_rect(fill = 'white', colour = 'white')) +
  theme(strip.background = element_rect(colour = "white", fill = "white"))+
  ylab(expression(paste("GWR Smoke PM"[2.5], " Concentration, Âµg/m^3" ))) +
  xlab("May 1st to Sep 30th in 2013") +
  theme(axis.line.x = element_line(color="black"),
        axis.line.y = element_line(color="black"))+
  theme(axis.text.x = element_text(angle = 90, hjust = 1))

@@

# smoke days where GWR smoke > 15
smoke_map <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#3964C3", high = "#dc2430") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
   theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties Affected by Smoke PM2.5 > 10Âµg/m^3") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA)) +
  geom_text_repel(data = centroids, aes(long, lat, label = rownames(centroids), group=NULL), size = 2.5)

smoke_map1 <- ggplot(or_smk_df, aes(x=long, y=lat, group=group)) +
  # fill with number of smoke days
  geom_polygon(aes(fill = smoke_days), alpha = 0.7) +
  scale_fill_gradient("Smoke-Impacted Days",
                      low = "#3964C3", high = "#dc2430") +
  # add county path on top
  geom_path() +
  facet_wrap(~smk_cut_method) +
   theme(strip.background = element_blank(),
       strip.text.x = element_blank()) +
  xlab("Longitude") +
  ylab("Latitude") +
  ggtitle("Oregon: Counties Affected by Smoke PM2.5 > 10Âµg/m^3") +
  theme(panel.background = element_rect(fill = 'white', colour = 'black'),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank(),
    strip.background = element_rect(colour=NA, fill=NA)) +
  geom_text(data = centroids, aes(long, lat, label = rownames(centroids), group=NULL), size = 2)

@@

For all of 2013, there were a total of 77 million claim records in the APAC dataset. The total number of insured SABA medication admission records in the APAC data set was about 232,665 in 2013 while during the wildfire season the number was only 24217. Table 1 showed the number and the age-specific and sex-specific strata.

@@

### Outcomes of four kinds (Not shown in paper)

@@

In Figure 3, we found the overall plot showed that when smoke concentration increases 10ug/m^3, the risk to get SABA fill for all respiratory outcomes using GWR method would increase about 7.5% significantly (OR: 1.077, 95% Confidence Interval [CI]: 1.065-1.088).

@@

In Figure 4, we found the plots showed that when smoke concentration increases 10ug/m^3, the risk to get SABA fill in asthma only category outcomes using GWR method would increase about 7.5% significantly (OR: 1.077, 95% CI: 1.060-1.095). For COPD only outcomes, no significant association was observed by GWR method (OR: 1.031, 95% CI: 0.995-1.067). When smoke concentration increases 10ug/m^3, the risk to get SABA fill in asthma and COPD category outcomes using GWR method would increase about 6% significantly (OR: 1.059, 95% CI: 1.017-1.104). when smoke concentration increases 10ug/m^3, the risk to get SABA fill in other category outcomes using GWR method would increase about 9.5% significantly (OR: 1.077, 95% Confidence Interval [CI]: 1.076-1.114).

@@

@@

Figure 5 showed association between a 10 ug/m^3 increase in smoke PM2.5 and risk for lagged days (0-7) of SABA fill events. When choosing the df of 5, the plot showed that the same day of fill with smoke exposure has the highest significant association, and the risk of filling SABA will increase 4% when the smoke PM2.5 increased 10 ug/m^3 significantly. But other lag days showed that pharmacy fills with lagged days did not has the significant association with smoke. And the association tended to decrease as lag goes.

@@

Figure 6 showed association between a 10 ug/m^e increase in smoke PM2.5 and risk for lagged days (0-7) of respiratory events. We focused on asthma and COPD. However, the lag days did not show significant associations. And the risks were fluctuated.

```{r DLM for disease respiratory, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum <- matrix(nrow = 12, ncol = 5)
cum[1,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])
colnames(cum) <- c("Outcomes",  "Cumulative Est", "Cumulative SE", "Lower 95% CI", "Upper 95% CI")

# knitr::kable(cum, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease asthma, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[2,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum2, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease pneumonia, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[3,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum3, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease acute_bronch, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[4,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum4, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease copd, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[5,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum5, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease cvd, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[6,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum6, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease isch_heart_dis, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[7,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum7, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease arrhythmia, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[8,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum8, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease heart_failure, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[9,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum9, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease cerbrovas_dis, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[10,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum10, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease myocardial_infarc, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[11,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum11, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r DLM for disease broken_arm, echo = FALSE, message=FALSE, warning=FALSE, include=FALSE}

@@

cum[12,2:5] <- cbind(cumulative, cumulative_se, cumulative_CI[1], cumulative_CI[2])

# knitr::kable(cum12, caption = paste0("Distributed lag 0-7 spline estimates, se and CI"))

```{r plot and dlm, echo=FALSE, message=FALSE, warning=FALSE}
plot_grid(p1, p2, p3, p4, p5, p6, p7, p8, p9, p10, p11, p12, ncol=4)

cum[,1] <- c("Respiratory", "Athma", "Pneumonia", "Acute bronch", "COPD", "cvd", "Isch heart disease", "Arrhythmia", "Heart failure", "Cerbrovas disease", "Myocardial infarction", "Broden arm")

tab <- htmlTable(txtRound(cum, digits = 3), 
         caption = "Association between a 10 ug/m^3 increase in smoke PM2.5  and health outcomes risks for lagged days",
         # row group by outcome
        #  rgroup = "Beta - 2 agonists",
        #  n.rgroup = c(rep(3, 1)), # 6 rows for each age cat for each outcome
         # column headers
         header = c("Outcomes", "Culmulative Est", "Culmulative SE", "Lower", "Upper"),
         # column spanner
         cgroup = c("", "95% CI"), 
         n.cgroup = c(3, 2),
         padding.rgroup = "&nbsp;&nbsp;",
         css.cell = "padding-left: 0.5em; padding-right: .5em;", # cell space
         align = "llcccc", # column alignment,
         tfoot="&dagger; Time-stratified: referent periods matched to events on same day of week within May to September fire season."
         ) # end table
